Limb-darkening and exoplanets II: Choosing the Best Law for Optimal Retrieval of Transit Parameters

### 2016-01-26 which_law_2_use.tex
Corrected typo in abstract. Will be uploaded to arXiv.

\begin{abstract}
Very precise measurements of exoplanet transit lightcurves both from ground and space based observatories make it now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. 
This strategy has been shown to give better results, as fixing the coefficients to theoretical values can give rise to important systematic 
errors which directly impact the physical properties of the system derived from such lightcurves such as the planetary radius. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler or 
better descriptions of model intensity profiles. In this work, we show that laws such as the 
logarithmic, square-root and three-parameter law do a better job that the quadratic and linear laws when deriving parameters from transit lightcurves, both in terms of 
bias and precision, for a wide range of situations. We therefore recommend to study which law to 
use on a case-by-case basis. We provide code to guide the decision of when to use each of these laws and select the optimal one in a 
mean-square error sense, which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
\end{abstract}

@@

It is evident from our results how the MSE evolves from being variance-dominated for low-noise lightcurves (rightmost part of the plot) to bias-dominated for high-noise 
lightcurves (leftmost part of the plot). This evolution is most evident for the linear law: for $N=100$ in-transit points, for example, the linear law attains the bias floor around 
$\approx100$ ppm. From here and for more precise lightcurves, the MSE of this law attains the constant value $\sim 10^{-6}$, which corresponds to the bias floor of 
$10^{-3}$, which for $p=0.1$ corresponds to the $1\%$ bias observed on our simulations on the past sub-section (see Figure~\ref{small_b_sims}). 
Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected with ease. For example, in our simulation, for $N=100$ in-transit points, 
the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense for lightcurves with noise levels between $\approx3000$ ppm to $\approx 1000$ ppm. 
At this last noise level, we see that the square-root law crosses the line of the logarithmic law, and this latter law attains the lowest MSE until $\approx 200$ ppm, where the 
quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\approx 200$ ppm until lightcurves with precisions of $\approx25$ ppm, a noise level at 
which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes the  points at which the transition among different limb-darkening 
laws occur due to the fact that the bias floor is attained faster as a consequence of the increased number of points. For example, the transition between the quadratic and three-parameter 
laws occurs for lower precision lightcurves for the case of $1000$ in-transit points (at $\approx 75$ ppm).

>>>>

\begin{abstract}
Very precise measurements of exoplanet transit lightcurves both from ground and space based observatories make it now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. 
This strategy has been shown to give better results, as fixing the coefficients to theoretical values can give rise to important systematic 
errors which directly impact the physical properties of the system derived from such lightcurves such as the planetary radius. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler or 
better descriptions of model intensity profiles. In this work, we show that laws such as the 
logarithmic, square-root and three-parameter law do a better job than the quadratic and linear laws when deriving parameters from transit lightcurves, both in terms of 
bias and precision, for a wide range of situations. We therefore recommend to study which law to 
use on a case-by-case basis. We provide code to guide the decision of when to use each of these laws and select the optimal one in a 
mean-square error sense, which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
\end{abstract}

@@

It is evident from our results how the MSE evolves from being variance-dominated for high-noise lightcurves (rightmost part of the plot) to bias-dominated for low-noise 
lightcurves (leftmost part of the plot). This evolution is most evident for the linear law: for $N=100$ in-transit points, for example, the linear law attains the bias floor around 
$\approx100$ ppm. From here and for more precise lightcurves, the MSE of this law attains the constant value $\sim 10^{-6}$, which corresponds to the bias floor of 
$10^{-3}$, which for $p=0.1$ corresponds to the $1\%$ bias observed on our simulations on the past sub-section (see Figure~\ref{small_b_sims}). 
Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected with ease. For example, in our simulation, for $N=100$ in-transit points, 
the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense for lightcurves with noise levels between $\approx3000$ ppm to $\approx 1000$ ppm. 
At this last noise level, we see that the square-root law crosses the line of the logarithmic law, and this latter law attains the lowest MSE until $\approx 200$ ppm, where the 
quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\approx 200$ ppm until lightcurves with precisions of $\approx25$ ppm, a noise level at 
which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes the  points at which the transition among different limb-darkening 
laws occur due to the fact that the bias floor is attained faster as a consequence of the increased number of points. For example, the transition between the quadratic and three-parameter 
laws occurs for lower precision lightcurves for the case of $1000$ in-transit points (at $\approx 75$ ppm).
